---
title: "JobProject"
author: "Ricky"
date: "12/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,out.width="0.9\\linewidth",dev="png",fig.align  = 'center')
warning = F
message = F
pacman::p_load(
dplyr,
tidytext,
ggplot2,
forcats,
tidyr,
stringr,
wordcloud2,
usmap,
ggmap,
leaflet,
gridExtra,
igraph,
ggraph
)
```

# Read Data
```{r}
listings_ST <- readRDS("listings_ST2.rds")
listings_DS <- readRDS("listings_DS2.rds")
register_google("AIzaSyC9ENZrkqlnOVQw0ndDsEe90KVaat5CxTs")
```

# Stop Words
```{r}
data(stop_words)
mystopwords <- tibble(word = c("data","required","position","including","skills","ability","u.s","NA",stop_words$word))
```

# Description: Count words
## Statistician
```{r}
text_description_ST <- tibble(text = listings_ST$description)
# text_description_ST

count_ST <- text_description_ST  %>%
  unnest_tokens(word, text) %>%
  anti_join(mystopwords) %>%
  count(word, sort = TRUE) %>%
  slice_max(n, n = 20) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word)) +
  geom_col(fill="steelblue",alpha = 0.5) +
  xlim(0, 2500) +
  scale_x_reverse() +
  scale_y_discrete(position = "right") +
  labs(y = NULL)

count_ST

cloud_ST <- text_description_ST  %>%
  unnest_tokens(word, text) %>%
  anti_join(mystopwords) %>%
  count(word, sort = TRUE) %>%
  filter(n > 50) %>%
  wordcloud2(size = 2, minRotation = -pi/6, maxRotation = -pi/6,  rotateRatio = 1)

# cloud_ST
```

## Data Scientist
```{r}
text_description_DS <- tibble(text = listings_DS$description)
# text_description_DS

count_DS <- text_description_DS  %>%
  unnest_tokens(word, text) %>%
  anti_join(mystopwords) %>%
  count(word, sort = TRUE) %>%
  slice_max(n, n = 20) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word)) +
  geom_col(fill="darkgreen",alpha = 0.5) +
  xlim(0, 2500) +
  labs(y = NULL)

count_DS

cloud_DS <- text_description_DS  %>%
  unnest_tokens(word, text) %>%
  anti_join(mystopwords) %>%
  count(word, sort = TRUE) %>%
  filter(n > 50) %>%
  wordcloud2(size = 2, minRotation = -pi/6, maxRotation = -pi/6,  rotateRatio = 1)

# cloud_DS
```

# Description: 2-grams
## Statistician
```{r}
bigrams_filtered <- listings_ST  %>% 
  filter(!is.na(description)) %>%
  unnest_tokens(bigram, description, token = "ngrams", n = 2) %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word) %>%
  filter(!word1 %in% mystopwords$word) %>%
  filter(!word2 %in% mystopwords$word) 
  

bigram_counts <- bigrams_filtered %>%
  count(word1, word2, sort = TRUE)

bigrams_united <- bigrams_filtered %>%
  unite(bigram, word1, word2, sep = " ")

bigrams_united %>% count(bigram, sort = TRUE) %>%
  filter(n > 100) %>%
  mutate(bigram = reorder(bigram, n)) %>%
  ggplot(aes(n, bigram)) +
  geom_col() +
  labs(y = NULL)

# igraph
bigram_graph <- bigram_counts %>%
  filter(n > 20) %>%
  graph_from_data_frame()

set.seed(2020)
ggraph(bigram_graph, layout = "fr") +
  geom_edge_link() +
  geom_node_point() +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1)

a <- grid::arrow(type = "closed", length = unit(.15, "inches"))

ggraph(bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  theme_void()


```

## Data Scientist
```{r}
bigrams_filtered <- listings_DS  %>% 
  filter(!is.na(description)) %>%
  unnest_tokens(bigram, description, token = "ngrams", n = 2) %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word) %>%
  filter(!word1 %in% mystopwords$word) %>%
  filter(!word2 %in% mystopwords$word) 
  
bigram_counts <- bigrams_filtered %>% 
  count(word1, word2, sort = TRUE)

bigrams_united <- bigrams_filtered %>%
  unite(bigram, word1, word2, sep = " ")

bigrams_united %>% count(bigram, sort = TRUE) %>%
  filter(n > 100) %>%
  mutate(bigram = reorder(bigram, n)) %>%
  ggplot(aes(n, bigram)) +
  geom_col() +
  labs(y = NULL)

# igraph
bigram_graph <- bigram_counts %>%
  filter(n > 20) %>%
  graph_from_data_frame()

set.seed(2020)
ggraph(bigram_graph, layout = "fr") +
  geom_edge_link() +
  geom_node_point() +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1)

a <- grid::arrow(type = "closed", length = unit(.15, "inches"))

ggraph(bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  theme_void()

```

# Question 2: Experience: How many years of experience are expected by company?
## Statistician
```{r}
Exp_year_ST <- str_extract_all(text_description_ST$text, "[0-9].+?year") %>% unlist()
Exp_year_ST <- 
  Exp_year_ST[which(nchar(Exp_year_ST) <= 10)] %>%
  str_extract_all("[[:digit:]]{1,2}") %>%
  unlist() %>%
  as.integer()
Exp_year_ST <- Exp_year_ST[which(Exp_year_ST <= 10)]
p_Exp_ST <- ggplot() +
  geom_histogram(data = NULL, aes(x = Exp_year_ST), binwidth =1,fill="steelblue",alpha = 0.5) +
  scale_x_continuous(breaks = 0:10)

# p_Exp_ST

```

## Data Scientist
```{r}
Exp_year_DS <- str_extract_all(text_description_DS$text, "[0-9].+?year") %>% unlist()
Exp_year_DS <- 
  Exp_year_DS[which(nchar(Exp_year_DS) <= 10)] %>%
  str_extract_all("[[:digit:]]{1,2}") %>%
  unlist() %>%
  as.integer()
Exp_year_DS <- Exp_year_DS[which(Exp_year_DS <= 10)]
p_Exp_DS <- ggplot() +
  geom_histogram(data = NULL, aes(x = Exp_year_DS), binwidth =1,fill="darkgreen",alpha = 0.5) +
  scale_x_continuous(breaks = 0:10)

# p_Exp_DS

```

# Question 3: Location: Where to find a Data Job?
## Statistician
```{r}
Loc_ST <- listings_ST %>% separate(location,c("city","state"), sep = ", ") 
Loc_ST_State <- na.omit(Loc_ST$state)
Loc_ST_State <- tibble(state = Loc_ST_State)
p_Loc_ST <- Loc_ST_State %>% count(state, sort = TRUE) %>% filter(n > 3) %>% ggplot() +
  geom_col(aes(x = reorder(state,-n), y = n), fill="steelblue",alpha = 0.5) +
  theme_bw() + 
  xlab("State") +   ylab("Count") + 
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5, vjust = 0.5), legend.position='none')

# p_Loc_ST
```

```{r}
# Statistician in MA
Loc_ST_City <- filter(Loc_ST,state == "MA")
Loc_ST_City <- na.omit(Loc_ST_City$city)
Loc_ST_City <- tibble(city = Loc_ST_City)
p_Loc_ST2_MA <- Loc_ST_City %>% count(city, sort = TRUE) %>% filter(n>1) %>% ggplot() +
  geom_col(aes(x = reorder(city,-n), y = n), fill="steelblue",alpha = 0.5) +
  theme_bw() + 
  xlab("MA_City") +   ylab("Count") + 
  theme(axis.text.x = element_text(angle = 20, hjust = 0.5, vjust = 0.5), legend.position='none')

# p_Loc_ST2_MA

# Statistician in CA
Loc_ST_City <- filter(Loc_ST,state == "CA")
Loc_ST_City <- na.omit(Loc_ST_City$city)
Loc_ST_City <- tibble(city = Loc_ST_City)
p_Loc_ST2_MA <- Loc_ST_City %>% count(city, sort = TRUE) %>% filter(n>1) %>% ggplot() +
  geom_col(aes(x = reorder(city,-n), y = n), fill="steelblue",alpha = 0.5) +
  theme_bw() + 
  xlab("CA_City") +   ylab("Count") + 
  theme(axis.text.x = element_text(angle = 20, hjust = 0.5, vjust = 0.5), legend.position='none')

# p_Loc_ST2_CA

```

## Data Scientist
```{r}
Loc_DS <- listings_DS %>% separate(location,c("city","state"), sep = ", ") 
Loc_DS_State <- na.omit(Loc_DS$state)
Loc_DS_State <- tibble(state = Loc_DS_State)
p_Loc_DS <- Loc_DS_State %>% count(state, sort = TRUE) %>% filter(n > 3) %>% ggplot() +
  geom_col(aes(x = reorder(state,-n), y = n), fill="darkgreen",alpha = 0.5) +
  theme_bw() + 
  xlab("State") +   ylab("Count") + 
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5, vjust = 0.5), legend.position='none')

# p_Loc_DS
```

```{r}
# Data Scientist in MA
Loc_DS_City <- filter(Loc_DS,state == "MA")
Loc_DS_City <- na.omit(Loc_DS_City$city)
Loc_DS_City <- tibble(city = Loc_DS_City)
p_Loc_DS2_MA <- Loc_DS_City %>% count(city, sort = TRUE) %>%  filter(n > 1) %>% ggplot() +
  geom_col(aes(x = reorder(city,-n), y = n), fill="darkgreen",alpha = 0.5) +
  theme_bw() + 
  xlab("MA_City") +   ylab("Count") + 
  theme(axis.text.x = element_text(angle = 20, hjust = 0.5, vjust = 0.5), legend.position='none')

# p_Loc_DS2_MA

# Data Scientist in CA
Loc_DS_City <- filter(Loc_DS,state == "CA")
Loc_DS_City <- na.omit(Loc_DS_City$city)
Loc_DS_City <- tibble(city = Loc_DS_City)
p_Loc_DS2_CA <- Loc_DS_City %>% count(city, sort = TRUE) %>%  filter(n > 1) %>% ggplot() +
  geom_col(aes(x = reorder(city,-n), y = n), fill="darkgreen",alpha = 0.5) +
  theme_bw() + 
  xlab("CA_City") +   ylab("Count") + 
  theme(axis.text.x = element_text(angle = 20, hjust = 0.5, vjust = 0.5), legend.position='none')

# p_Loc_DS2_CA
```


# Question 4: Word Count/Clound under Location MA/CA
## Statistician
```{r}
ST_MA_CA <- filter(Loc_ST,state %in% c("MA","CA"))

ST_MA_CA <- tibble(ST_MA_CA)

count_ST_Loc <- ST_MA_CA  %>%
  unnest_tokens(word, description, token = "words") %>%
  anti_join(mystopwords) %>%
  group_by(state) %>%
  count(word, sort = TRUE) %>%
  slice_max(n, n = 20) %>%
  ungroup()

p_ST_Loc_CA <- filter(count_ST_Loc,state == "CA") %>%
  ggplot(aes(x = n, y = reorder(word,n))) +
  geom_col(fill = "orange", alpha = 0.5,show.legend = FALSE) +
  labs(x = "CA", y = NULL)

p_ST_Loc_MA <- filter(count_ST_Loc,state == "MA") %>%
  ggplot(aes(x = n, y = reorder(word,n))) +
  geom_col(fill = "red", alpha = 0.5, show.legend = FALSE) +
  labs(x = "MA", y = NULL)

# grid.arrange(p_ST_Loc_CA, p_ST_Loc_MA, ncol=2)

```

## Data Scientist
```{r}
DS_MA_CA <- filter(Loc_DS,state %in% c("MA","CA"))

DS_MA_CA <- tibble(DS_MA_CA)

count_DS_Loc <- DS_MA_CA  %>%
  unnest_tokens(word, description, token = "words") %>%
  anti_join(mystopwords) %>%
  group_by(state) %>%
  count(word, sort = TRUE) %>%
  slice_max(n, n = 20) %>%
  ungroup()

p_DS_Loc_CA <- filter(count_DS_Loc,state == "CA") %>%
  ggplot(aes(x = n, y = reorder(word,n))) +
  geom_col(fill = "orange", alpha = 0.5,show.legend = FALSE) +
  labs(x = "CA", y = NULL)

p_DS_Loc_MA <- filter(count_DS_Loc,state == "MA") %>%
  ggplot(aes(x = n, y = reorder(word,n))) +
  geom_col(fill = "red", alpha = 0.5, show.legend = FALSE) +
  labs(x = "MA", y = NULL)

# grid.arrange(p_DS_Loc_CA, p_DS_Loc_MA, ncol=2)
```

# Question 5: Company: Who is providing Data Job?
## Statistician
```{r}
count_ST_Comp <- tibble(text = listings_ST$company)  %>%
  count(text, sort = TRUE) %>%
  filter(n > 5) %>%
  mutate(text = reorder(text, n)) %>%
  ggplot(aes(n, text)) +
  geom_col() +
  labs(y = NULL)

# count_ST_Comp

```

## Data Scientist
```{r}
count_DS_Comp <- tibble(text = listings_DS$company)  %>%
  count(text, sort = TRUE) %>%
  filter(n > 2) %>%
  mutate(text = reorder(text, n)) %>%
  ggplot(aes(n, text)) +
  geom_col() +
  labs(y = NULL)

# count_DS_Comp
```

# Mapping
## Statistician
```{r}
Link <- paste0('<a href = ',listings_ST$link,'> Details from Indeed </a>')
i_popup <- paste0("<strong>Titel: </strong>", listings_ST$title, "<br>", 
                  "<strong>Company: </strong>", listings_ST$company, "<br>", 
                  "<strong>Location: </strong>", listings_ST$address, "<br>",
                  "<strong>Job Link: </strong>", Link)

LL <- listings_ST[8:9]
Mapping_ST <- LL %>%
  leaflet() %>%
  addTiles() %>%
  setView(-71.0588, 42.36, zoom = 10) %>%
  addMarkers(clusterOptions = markerClusterOptions(),popup=i_popup)
```

## Data Scientist
```{R}
Link <- paste0('<a href = ',listings_DS$link,'> Details from Indeed </a>')
i_popup <- paste0("<strong>Titel: </strong>", listings_DS$title, "<br>", 
                  "<strong>Company: </strong>", listings_DS$company, "<br>", 
                  "<strong>Location: </strong>", listings_DS$address, "<br>",
                  "<strong>Job Link: </strong>", Link)

LL <- listings_DS[8:9]
Mapping_DS <- LL %>%
  leaflet() %>%
  addTiles() %>%
  setView(-71.0588, 42.36, zoom = 10) %>%
  addMarkers(clusterOptions = markerClusterOptions(),popup=i_popup)

```



