---
title: "Search for a Data Job - Final Project"
author: "Ricky"
date: "12/13/2020"
output:
  revealjs::revealjs_presentation:
    theme: solarized
    transition: default
    css: leaflet-reveal.css
    center: false
    self_contained: false
    reveal_plugins: ["menu"]
    reveal_options:
      menu:
        numbers: true
      slideNumber: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
warning = F
message = F
pacman::p_load(
dplyr,
tidytext,
ggplot2,
forcats,
tidyr,
stringr,
wordcloud,
usmap,
ggmap,
leaflet,
gridExtra,
kableExtra,
igraph,
ggraph
)
```

```{r include=FALSE}
# Read Data
listings_ST <- readRDS("listings_ST2.rds")
listings_DS <- readRDS("listings_DS2.rds")
# register_google("AIzaSyC9ENZrkqlnOVQw0ndDsEe90KVaat5CxTs")

```

# Search for a Data Job

Nowadays, we have two different types of title for Data Job, one is Statistician, one is Data Scientist. What are the difference between these two kind of title?  

Here are some questions to be answered in this project:  
1. Descriptions: Is there any difference in the Job Descriptions?  
2. Experience: How many years of experience are expected by companies?  
3. Location: Where to find a Data Job?  
4. Location: Word Count/Cloud between different location (MA/CA)  
5. Company: Who is providing Data Job?  
6. Mapping the Jobs  

# Extract data from Indeed

In the website of Indeed: <https://www.indeed.com/>, we can search for Job information with keywords.  
Extract data with keywords  **Statistician** and **Data Scientist**, get information of Job Title, Company, Location, Job Link, Job Description.  
Take Statistician as example:  

```{r echo=FALSE}
kable(head(listings_ST[,c(1:3,5:6)],10),col.names = c("Title","Company","Location","Link","Description"),"html",align = "c") %>%
  kable_styling(font_size = 11) %>%
    scroll_box(width = "105%", height = "400px")
```

# 1. Difference in Job Descriptions.

- Word Count

```{r include=FALSE}
# Stop Words
data(stop_words)
mystopwords <- tibble(word = c("data","required","position","including","skills","ability","u.s","NA",stop_words$word))
```

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width = 11, fig.height=4.5, fig.align='center'}
# text_description_ST
text_description_ST <- tibble(text = listings_ST$description)
count_ST <- text_description_ST  %>%
  unnest_tokens(word, text) %>%
  anti_join(mystopwords) %>%
  count(word, sort = TRUE) %>%
  slice_max(n, n = 20) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word)) +
  geom_col(fill="steelblue",alpha = 0.5) +
  xlim(0, 2500) +
  scale_x_reverse() +
  scale_y_discrete(position = "right") +
  ggtitle("Statistician") +
  labs(x = NULL) +
  labs(y = NULL)

# text_description_DS
text_description_DS <- tibble(text = listings_DS$description)
count_DS <- text_description_DS  %>%
  unnest_tokens(word, text) %>%
  anti_join(mystopwords) %>%
  count(word, sort = TRUE) %>%
  slice_max(n, n = 20) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word)) +
  geom_col(fill="darkgreen",alpha = 0.5) +
  xlim(0, 2500) +
  ggtitle("Data Scientist") +
  labs(x = NULL) +
  labs(y = NULL)

grid.arrange(count_ST,count_DS, nrow = 1, ncol = 2)

```

From the plots, we can find that both of them have a high frequency words like experience, analysis and statistical. But also have some special words. For example:  
**Statistician:** Research, management, clinical, design...  
**Data Scientist:** Learning, machine, tools, modeling, techniques...

----

- Word Cloud of Statistician  

The left one is the cloud of  Statistician, the right one is the cloud of Data Scientist.  
```{r echo=FALSE,message=FALSE, warning=FALSE, fig.width = 12, fig.height=6, fig.align='center'}

par(mfrow=c(1,2))

cloud_ST <- text_description_ST  %>%
  unnest_tokens(word, text) %>%
  anti_join(mystopwords) %>%
  count(word, sort = TRUE) %>%
  filter(n > 100)

set.seed(2020)
  p1 <- wordcloud(words = cloud_ST$word, freq = cloud_ST$n, min.freq = 1, max.words = 150, colors = brewer.pal(8, 'Paired'), random.order = FALSE,rot.per=0.35)
  

cloud_DS <- text_description_DS  %>%
   unnest_tokens(word, text) %>%
   anti_join(mystopwords) %>%
   count(word, sort = TRUE) %>%
   filter(n > 100) 

set.seed(2020)
  p2 <- wordcloud(words = cloud_DS$word, freq = cloud_DS$n, min.freq = 1, max.words = 150, colors = brewer.pal(8, 'Dark2'), random.order = FALSE,rot.per=0.35,scale=c(2.5,0.75))

```

----

- 2-grams words 

```{r echo=FALSE, fig.width = 10, fig.height=4.5, fig.align='center'}
bigrams_filtered_ST <- listings_ST  %>% 
  filter(!is.na(description)) %>%
  unnest_tokens(bigram, description, token = "ngrams", n = 2) %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word) %>%
  filter(!word1 %in% mystopwords$word) %>%
  filter(!word2 %in% mystopwords$word) 

bigram_counts_ST <- bigrams_filtered_ST %>%
  count(word1, word2, sort = TRUE)

bigrams_united_ST <- bigrams_filtered_ST %>%
  unite(bigram, word1, word2, sep = " ")

p_2g_ST <- bigrams_united_ST %>% count(bigram, sort = TRUE) %>%
  slice_max(n, n = 20) %>%
  mutate(bigram = reorder(bigram, n)) %>%
  ggplot(aes(n, bigram)) +
  geom_col(fill="steelblue",alpha = 0.5) +
  scale_x_reverse() +
  scale_y_discrete(position = "right") +
  ggtitle("Statistician") +
  labs(x = NULL) +
  labs(y = NULL)

# p_2g_ST

bigrams_filtered_DS <- listings_DS  %>% 
  filter(!is.na(description)) %>%
  unnest_tokens(bigram, description, token = "ngrams", n = 2) %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word) %>%
  filter(!word1 %in% mystopwords$word) %>%
  filter(!word2 %in% mystopwords$word) 

bigram_counts_DS <- bigrams_filtered_DS %>%
  count(word1, word2, sort = TRUE)

bigrams_united_DS <- bigrams_filtered_DS %>%
  unite(bigram, word1, word2, sep = " ")

p_2g_DS <- bigrams_united_DS %>% count(bigram, sort = TRUE) %>%
  slice_max(n, n = 20) %>%
  mutate(bigram = reorder(bigram, n)) %>%
  ggplot(aes(n, bigram)) +
  geom_col(fill="darkgreen",alpha = 0.5) +
  ggtitle("Data Scientist") +
  labs(x = NULL) +
  labs(y = NULL)

# p_2g_DS

grid.arrange(p_2g_ST,p_2g_DS, nrow = 1, ncol = 2)
```

From the 2-grams plots, we can find some special topic in the descriptions. Most of the companies will mention "Opportunity", "Race", "Sexual" problems.  
Also, we can tell that **Clinical** will give more "Statistician" title, and may focus on qualified applicants.And "Statistician" will work on methods, research, development...  
But for "Data Scientist", they are expected to gain "Computer science", and work on deep learning, modeling...

----

- Network plots  

Also give network plots of these two titles. The left one is for Statistician, and right one is for Data Scientist.

```{r echo=FALSE,message=FALSE, warning=FALSE, fig.width = 16, fig.height=8, fig.align='center'}

# igraph_ST
bigram_graph_ST <- bigram_counts_ST %>%
  filter(n > 20) %>%
  graph_from_data_frame()

set.seed(2020)
a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
bigram_graph_ST <- ggraph(bigram_graph_ST, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "steelblue",alpha = 0.5, size = 3) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  theme_void()

# bigram_graph_ST

# igraph_DS
bigram_graph_DS <- bigram_counts_DS %>%
  filter(n > 20) %>%
  graph_from_data_frame()

set.seed(2020)
bigram_graph_DS <- ggraph(bigram_graph_DS, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "steelblue",alpha = 0.5, size = 3) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  theme_void()

# bigram_graph_DS
grid.arrange(arrangeGrob(bigram_graph_ST,bigram_graph_DS, nrow = 1, ncol = 2), heights = 7, widths = 9 )
```


# Question 2: Experience requirement

As we can see, the word "Experience" is the most frequently mentioned one in the description. How many years of experience are expected by the companies?

```{r echo=FALSE,message=FALSE, warning=FALSE, fig.width = 11, fig.height=4.5, fig.align='center'}
Exp_year_ST <- str_extract_all(text_description_ST$text, "[0-9].+?year") %>% unlist()
Exp_year_ST <- 
  Exp_year_ST[which(nchar(Exp_year_ST) <= 10)] %>%
  str_extract_all("[[:digit:]]{1,2}") %>%
  unlist() %>%
  as.integer()
Exp_year_ST <- Exp_year_ST[which(Exp_year_ST <= 10)]

p_Exp_ST <- ggplot() +
  geom_histogram(data = NULL, aes(x = Exp_year_ST), binwidth =1,fill="steelblue",alpha = 0.5) + 
  geom_vline(aes(xintercept=mean(Exp_year_ST)),linetype=5,col="red") +
  xlab("Expect years for Statistician") +
  ylab("Count of Job Information") +
  scale_x_continuous(breaks = 0:10)

# p_Exp_ST

Exp_year_DS <- str_extract_all(text_description_DS$text, "[0-9].+?year") %>% unlist()
Exp_year_DS <- 
  Exp_year_DS[which(nchar(Exp_year_DS) <= 10)] %>%
  str_extract_all("[[:digit:]]{1,2}") %>%
  unlist() %>%
  as.integer()
Exp_year_DS <- Exp_year_DS[which(Exp_year_DS <= 10)]

p_Exp_DS <- ggplot() +
  geom_histogram(data = NULL, aes(x = Exp_year_DS), binwidth =1,fill="darkgreen",alpha = 0.5) +
  geom_vline(aes(xintercept=mean(Exp_year_DS)),linetype=5,col="red") +
  xlab("Expect years for Data Scientist") +
  ylab(NULL)+
  scale_x_continuous(breaks = 0:10)

# p_Exp_DS

grid.arrange(p_Exp_ST,p_Exp_DS, nrow = 1, ncol = 2)
```

From the plots, we can tell that most of the companies are expected for 1-3 years working experience, but for Statisticians, there is another high expect years, 5 years. 

# Question 3: Job location

- State Location

Look at the location distribution, we can find that most of the companies are located at Massachusetts and California.

```{r echo=FALSE,message=FALSE, warning=FALSE, fig.width = 11, fig.height=5, fig.align='center'}
Loc_ST <- listings_ST %>% separate(location,c("city","state"), sep = ", ") 
Loc_ST_State <- na.omit(Loc_ST$state)
Loc_ST_State <- tibble(state = Loc_ST_State)
p_Loc_ST <- Loc_ST_State %>% count(state, sort = TRUE) %>% filter(n > 3) %>% ggplot() +
  geom_col(aes(x = reorder(state,-n), y = n), fill="steelblue",alpha = 0.5) +
  theme_bw() + 
  xlab("Statistician") +   ylab("Count of Job Information") + 
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5, vjust = 0.5), legend.position='none')

# p_Loc_ST

Loc_DS <- listings_DS %>% separate(location,c("city","state"), sep = ", ") 
Loc_DS_State <- na.omit(Loc_DS$state)
Loc_DS_State <- tibble(state = Loc_DS_State)
p_Loc_DS <- Loc_DS_State %>% count(state, sort = TRUE) %>% filter(n > 3) %>% ggplot() +
  geom_col(aes(x = reorder(state,-n), y = n), fill="darkgreen",alpha = 0.5) +
  theme_bw() + 
  xlab("Data Scientist") +   ylab(NULL) + 
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5, vjust = 0.5), legend.position='none')

# p_Loc_DS

grid.arrange(p_Loc_ST,p_Loc_DS, nrow = 1, ncol = 2)

```

----

- Look at the city distribution of MA and CA

For statisticians, working opportunities concentrated at Massachusetts, especially Boston. 

```{r echo=FALSE,message=FALSE, warning=FALSE, fig.width = 11, fig.height=6, fig.align='center'}
# Statistician in MA
Loc_ST_City <- filter(Loc_ST,state == "MA")
Loc_ST_City <- na.omit(Loc_ST_City$city)
Loc_ST_City <- tibble(city = Loc_ST_City)
p_Loc_ST2_MA <- Loc_ST_City %>% count(city, sort = TRUE) %>% filter(n>1) %>% ggplot() +
  geom_col(aes(x = reorder(city,-n), y = n), fill="steelblue",alpha = 0.5) +
  theme_bw() + 
  xlab("MA_City") +   ylab("Count") + 
  theme(axis.text.x = element_text(angle = 20, hjust = 0.5, vjust = 0.5), legend.position='none')

# p_Loc_ST2_MA

# Statistician in CA
Loc_ST_City <- filter(Loc_ST,state == "CA")
Loc_ST_City <- na.omit(Loc_ST_City$city)
Loc_ST_City <- tibble(city = Loc_ST_City)
p_Loc_ST2_CA <- Loc_ST_City %>% count(city, sort = TRUE) %>% filter(n>1) %>% ggplot() +
  geom_col(aes(x = reorder(city,-n), y = n), fill="steelblue",alpha = 0.5) +
  theme_bw() + 
  xlab("CA_City") +   ylab(NULL) + 
  theme(axis.text.x = element_text(angle = 20, hjust = 0.5, vjust = 0.5), legend.position='none')

# p_Loc_ST2_CA

grid.arrange(p_Loc_ST2_MA,p_Loc_ST2_CA, nrow = 1, ncol = 2)

```

----

When it turns to Data Scientists, more working opportunities can be find in California, especially San Francisco. 

```{r echo=FALSE,message=FALSE, warning=FALSE, fig.width = 11,  fig.height=6, fig.align='center'}
# Data Scientist in MA
Loc_DS_City <- filter(Loc_DS,state == "MA")
Loc_DS_City <- na.omit(Loc_DS_City$city)
Loc_DS_City <- tibble(city = Loc_DS_City)
p_Loc_DS2_MA <- Loc_DS_City %>% count(city, sort = TRUE) %>%  filter(n > 1) %>% ggplot() +
  geom_col(aes(x = reorder(city,-n), y = n), fill="darkgreen",alpha = 0.5) +
  theme_bw() + 
  xlab("MA_City") +   ylab("Count") + 
  theme(axis.text.x = element_text(angle = 20, hjust = 0.5, vjust = 0.5), legend.position='none')

# p_Loc_DS2_MA

# Data Scientist in CA
Loc_DS_City <- filter(Loc_DS,state == "CA")
Loc_DS_City <- na.omit(Loc_DS_City$city)
Loc_DS_City <- tibble(city = Loc_DS_City)
p_Loc_DS2_CA <- Loc_DS_City %>% count(city, sort = TRUE) %>%  filter(n > 1) %>% ggplot() +
  geom_col(aes(x = reorder(city,-n), y = n), fill="darkgreen",alpha = 0.5) +
  theme_bw() + 
  xlab("CA_City") +   ylab(NULL) + 
  theme(axis.text.x = element_text(angle = 20, hjust = 0.5, vjust = 0.5), legend.position='none')

# p_Loc_DS2_CA

grid.arrange(p_Loc_DS2_MA,p_Loc_DS2_CA, nrow = 1, ncol = 2)
```


# Question 4: Difference by Location

- Statistician

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width = 11,  fig.height=5, fig.align='center'}
ST_MA_CA <- filter(Loc_ST,state %in% c("MA","CA"))

ST_MA_CA <- tibble(ST_MA_CA)

count_ST_Loc <- ST_MA_CA  %>%
  unnest_tokens(word, description, token = "words") %>%
  anti_join(mystopwords) %>%
  group_by(state) %>%
  count(word, sort = TRUE) %>%
  slice_max(n, n = 20) %>%
  ungroup()

p_ST_Loc_CA <- filter(count_ST_Loc,state == "CA") %>%
  ggplot(aes(x = n, y = reorder(word,n))) +
  geom_col(fill = "orange", alpha = 0.5,show.legend = FALSE) +
  scale_x_reverse() +
  scale_y_discrete(position = "right") +
  ggtitle("CA") +
  xlab(NULL) + ylab(NULL)

p_ST_Loc_MA <- filter(count_ST_Loc,state == "MA") %>%
  ggplot(aes(x = n, y = reorder(word,n))) +
  geom_col(fill = "red", alpha = 0.5, show.legend = FALSE) +
  ggtitle("MA") +
  xlab(NULL) + ylab(NULL)

grid.arrange(p_ST_Loc_CA, p_ST_Loc_MA, ncol=2)

```

----

- Data Scientist

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width = 11,  fig.height=5, fig.align='center'}
DS_MA_CA <- filter(Loc_DS,state %in% c("MA","CA"))

DS_MA_CA <- tibble(DS_MA_CA)

count_DS_Loc <- DS_MA_CA  %>%
  unnest_tokens(word, description, token = "words") %>%
  anti_join(mystopwords) %>%
  group_by(state) %>%
  count(word, sort = TRUE) %>%
  slice_max(n, n = 20) %>%
  ungroup()

p_DS_Loc_CA <- filter(count_DS_Loc,state == "CA") %>%
  ggplot(aes(x = n, y = reorder(word,n))) +
  geom_col(fill = "orange", alpha = 0.5,show.legend = FALSE) +
  scale_x_reverse() +
  scale_y_discrete(position = "right") +
  ggtitle("CA") +
  xlab(NULL) + ylab(NULL)

p_DS_Loc_MA <- filter(count_DS_Loc,state == "MA") %>%
  ggplot(aes(x = n, y = reorder(word,n))) +
  geom_col(fill = "red", alpha = 0.5, show.legend = FALSE) +
  ggtitle("MA") +
  xlab(NULL) + ylab(NULL)

grid.arrange(p_DS_Loc_CA, p_DS_Loc_MA, ncol=2)
```

Look at the two plots above, we will tell that there is not a big difference between locations.


# Question 5: Who is providing Data Job

For Statisticians, Natera provided most opportunities, and most of the following companies are health industry companies, like Bristol Myers Squibb, Takeda Pharmaceuticals.

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width = 11,  fig.height=5, fig.align='center'}
count_ST_Comp <- tibble(text = listings_ST$company)  %>%
  count(text, sort = TRUE) %>%
  # filter(n > 5) %>%
  slice_max(n, n = 10) %>%
  mutate(text = reorder(text, n)) %>%
  ggplot(aes(n, text)) +
  geom_col(fill="steelblue",alpha = 0.5) +
  # scale_x_reverse() +
  # scale_y_discrete(position = "right") +
  ggtitle("Statistician") +
  xlab(NULL) +   ylab(NULL)

count_ST_Comp
```

----

However, except CVS, most of the Data Scientist positions come from technical companies, like Apple, Microsoft and IBM.

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width = 11,  fig.height=5, fig.align='center'}
count_DS_Comp <- tibble(text = listings_DS$company)  %>%
  count(text, sort = TRUE) %>%
  # filter(n > 2) %>%
  slice_max(n, n = 10) %>%
  mutate(text = reorder(text, n)) %>%
  ggplot(aes(n, text)) +
  geom_col(fill="darkgreen",alpha = 0.5) +
  ggtitle("Data Scientist") +
  xlab(NULL) +   ylab(NULL)

count_DS_Comp

# grid.arrange(count_ST_Comp, count_DS_Comp, ncol=2)
```

# Look at the Jobs in Map

- Statistician

```{r echo=FALSE, message=FALSE, warning=FALSE}
Link <- paste0('<a href = ',listings_ST$link,'> Details from Indeed </a>')
i_popup <- paste0("<strong>Titel: </strong>", listings_ST$title, "<br>", 
                  "<strong>Company: </strong>", listings_ST$company, "<br>", 
                  "<strong>Location: </strong>", listings_ST$address, "<br>",
                  "<strong>Job Link: </strong>", Link)

LL <- listings_ST[8:9]
Mapping_ST <- LL %>%
  leaflet() %>%
  addTiles() %>%
  setView(-78, 40, zoom = 6) %>%
  addMarkers(clusterOptions = markerClusterOptions(),popup=i_popup)

Mapping_ST
```

----

- Data Scientist

```{R echo=FALSE, message=FALSE, warning=FALSE}
Link <- paste0('<a href = ',listings_DS$link,'> Details from Indeed </a>')
i_popup <- paste0("<strong>Titel: </strong>", listings_DS$title, "<br>", 
                  "<strong>Company: </strong>", listings_DS$company, "<br>", 
                  "<strong>Location: </strong>", listings_DS$address, "<br>",
                  "<strong>Job Link: </strong>", Link)

LL <- listings_DS[8:9]
Mapping_DS <- LL %>%
  leaflet() %>%
  addTiles() %>%
  setView(-78, 40, zoom = 6) %>%
  addMarkers(clusterOptions = markerClusterOptions(),popup=i_popup)

Mapping_DS
```

Note: You can also get Job Details by click the link on the markers in the maps.

# Findings and Conclusion

# Inference